Declarative Integration of Interactive 3D Graphics into the World-Wide Web:\\Principles, Current Approaches, and Research Agenda

### 2013-04-29 Web3D2013-Dec3D/paper.tex
Uncommented Acknowledgements section and started with the DFKI Acknowledgements.
Update to Acknowledgements

%\section*{Acknowledgements}

>>>>

\section*{Acknowledgements}
The research presented in this paper has been supported by the EU projects VERVE\footnote{http://www.verveconsortium.eu/} and FI-CONTENT, the BMBF project EMERGENT, the Intel Visual Computing Institute, the SFI's Lion2 and EI's Copernicus projects, and the Villes Transparentes project.
